---
title: "Regression Analysis"
author: "Group 4"
date: "3/7/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

## Hypothesis 1

Our group decided to test out 2 hypothesis for this project. This is the document for our first hypothesis.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = "allow")
```

## Read input files from github

Get the link which has the merged data from github, then read the csv file and save it as a dataframe in R for analysis.

```{r, echo=TRUE}
link='https://raw.githubusercontent.com/Public-Policy-COVID/students_merge/main/Merged_data.csv'
myFile=url(link)
fromPy=read.csv(file = myFile)
```

# Summary results of merged data

In order to understand our merged dataset, we need to know some of the basic statistical summary for it. 

```{r, echo=TRUE}
summary(fromPy)
```

## Test hypothesis

We use regression when we have a continuous outcome or dependent variable, and a set of independent variables which can be of different types.

Run a regression to test the hypothesis that as number of hospitals, number of hospital beds and total_population increases, covid deaths increase and as mask score increases covid deaths decrease.

We use the glm function in R to run a linear regression.

```{r, echo=TRUE}
hypo1 = formula(Deaths_COVID~ Number_of_hospitals+Number_of_beds+mask_score+total_population)
gauss1=glm(hypo1,
           data = fromPy,
           family = 'gaussian')
```

See the results of our linear regression.

```{r, echo=TRUE}
summary(gauss1)
```

Get R squared of the model. R-squared is the percentage of the dependent variable variation that a linear model explains. R-squared helps us decide how effective this model is and compare it with other hypothesis as well. 

```{r, echo=TRUE}

library(rsq)
rsq(gauss1,adj=T)
```

## Summary plots

In order to visualize the results of our hypothesis and the dependent variables, we use different summary plots. 

Plotting the regression coefficients.

```{r, echo=TRUE}
# Summary plots
library(dotwhisker)
dwplot(gauss1,by_2sd = F)
```

Margin plot for number of hospitals variable.

```{r, echo=TRUE}
library(margins)
cplot(gauss1,'Number_of_hospitals')
```

Margin plot for number of beds variable.

```{r, echo=TRUE}
cplot(gauss1,'Number_of_beds')
```

Margin plot for mask score variable.

```{r, echo=TRUE}
cplot(gauss1,'mask_score')
```

Margin plot for total population variable.

```{r, echo=TRUE}
cplot(gauss1,'total_population')
```

Plot interaction between variables.

```{r, echo=TRUE}
persp(gauss1)
```
